### 2023-08-08 resilience.tex
Removing unecessary abreviation precisions

\problemx{resilience problem (RP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $\Safe, \Bad \subseteq S$.}
{$\Bad \longrightarrow^{*} \Safe$ ?\newline}

@@

\problemx{$k$-resilience problem (kRP)}
{A transition system $\mathscr{S}=(S,\rightarrow), k \in \mathbb{N}$ and two sets $\Safe, \Bad \subseteq S$.}
{$\Bad \longrightarrow^{\leq k} \Safe$ ?\newline}

\problemx{bounded resilience problem (BRP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $\Safe, \Bad \subseteq S$.}
%{$\exists k \geq 0 ~ \forall s' \in D ~ s \rightarrow^* s' \implies \exists s'' \in U ~ s' \rightarrow^{\leq k} s''$ ?\newline}
{$\exists k \geq 0$ such that $\mathscr{S}$ is %uniformely
 $k$-resilient ?\newline}

>>>>

\problemx{Resilience}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $\Safe, \Bad \subseteq S$.}
{$\Bad \longrightarrow^{*} \Safe$ ?\newline}

@@

\problemx{$k$-resilience problem}
{A transition system $\mathscr{S}=(S,\rightarrow), k \in \mathbb{N}$ and two sets $\Safe, \Bad \subseteq S$.}
{$\Bad \longrightarrow^{\leq k} \Safe$ ?\newline}

\problemx{Bounded resilience}
{A transition system $\mathscr{S}=(S,\rightarrow)$ and two sets $\Safe, \Bad \subseteq S$.}
%{$\exists k \geq 0 ~ \forall s' \in D ~ s \rightarrow^* s' \implies \exists s'' \in U ~ s' \rightarrow^{\leq k} s''$ ?\newline}
{$\exists k \geq 0$ such that $\mathscr{S}$ is %uniformely
 $k$-resilient ?\newline}

### 2023-08-08 state-resilience.tex
Removing unecessary abreviation precisions

\problemx{State-resilience problem (SRP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$, $s \in S$ and $\Safe \subseteq S$.}
% {$\Bad \cap \post^*(s)  \rightarrow^{*} \Safe $ ? \newline}
{$\post^*(s)  \rightarrow^{*} \Safe $ ? \newline}

\problemx{$k$-state-resilience problem (kSRP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$, $s \in S$, $k \geq 0$ and $\Safe \subseteq S$.}
% { $\Bad \cap \post^*(s) \longrightarrow^{\leq k} \Safe$ ?  \newline}
{ $\post^*(s) \longrightarrow^{\leq k} \Safe$ ?  \newline}

\problemx{bounded-state-resilience problem (BSRP)}
{A transition system $\mathscr{S}=(S,\rightarrow)$, $s \in S$ and $\Safe \subseteq S$.}
{$\exists k \geq 0$ such that $\mathscr{S}$ is $k$-state-resilient ?\newline}

>>>>

\problemx{State-resilience}
{A transition system $\mathscr{S}=(S,\rightarrow)$, $s \in S$ and $\Safe \subseteq S$.}
% {$\Bad \cap \post^*(s)  \rightarrow^{*} \Safe $ ? \newline}
{$\post^*(s)  \rightarrow^{*} \Safe $ ? \newline}

\problemx{$k$-state-resilience}
{A transition system $\mathscr{S}=(S,\rightarrow)$, $s \in S$, $k \geq 0$ and $\Safe \subseteq S$.}
% { $\Bad \cap \post^*(s) \longrightarrow^{\leq k} \Safe$ ?  \newline}
{ $\post^*(s) \longrightarrow^{\leq k} \Safe$ ?  \newline}

\problemx{bounded-state-resilience}
{A transition system $\mathscr{S}=(S,\rightarrow)$, $s \in S$ and $\Safe \subseteq S$.}
{$\exists k \geq 0$ such that $\mathscr{S}$ is $k$-state-resilient ?\newline}
